Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
extract EB estimates and RE for personality

summary(SAM1)
(SAM1)

>>>>

sjPlot::tab_model(SAM1)

## save random effects
lapply(ranef(SAM1), write.table, 
       append = TRUE, 
       file = "raneff from SAM1 for TRT.csv")

## extract empirical bayesian estimates
EBTRTtar <- ranef(SAM1)$TarUn
colnames(EBTRTtar)<-c("Intercept","TSR","Norm")
EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
summary(EBTRTtar)
sapply(EBTRTtar,sd)
